NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-05-17 Manuscript/manuscriptPS.tex
Add plot comparing POPS and OPPS from MacRog simulations.
Update preliminary figure summarising experimental results

Figs. \ref{PShgSIGNSsimpson} and \ref{glycerolNMR} summarize the experimental NMR results for POPS
bilayer sample. \todo{New figure, probably combining Figs. \ref{PShgSIGNSsimpson} and \ref{glycerolNMR}, should
be done. This discussion to be finished after this.}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=6.0cm]{../Figs/PShgSIGNSsimpson.pdf}
  \caption{\label{PShgSIGNSsimpson}
    (a) The headgroup region of the INEPT spectrum where alpha and beta are
    identified.
    (b) The R-PDLF slices for alpha and beta showing one single
    splitting for beta (which gives an order parameter equal to 0.12), and for alpha a superposition
    of a large splitting (order parameter equal to 0.09) and a very small splitting which cannot
    resolved with the available resolution.
    (c) Points with error bars are the experimental SDROSS data.
    The thick lines are SIMPSON simulations.
    The S-DROSS slice for beta clearly shows that the order parameter is negative,
    which is confirmed by SIMPSON simulations using the order parameter value of -0.12.
    The S-DROSS slice for alpha suggests that the higher order parameter is positive
    and the deviation towards negative values in the longer t1 times suggests
    that the smaller order parameter is negative.
    This is confirmed by SIMPSON simulation using value of 0.09
    for the larger alpha order parameter and the value of -0.02 for
    smaller (black curve). The value for the smaller
    alpha order parameter for SIMPSON calculation was taken from Fig 3 in Ref. \citenum{roux91},
    because resolution in 13C NMR experiments was nor high enough to determine
    numerical value for this. The S-DROSS curve from SIMPSON simulation with positive value
    for the smaller order parameter gave did not agree with experiments (dashed grey),
    confirming the interpretation that the smaller order parameter is negative.
  }
  \todo{Maybe we should combine this with \ref{glycerolNMR}}
\end{figure}

\begin{figure}[!htb]
  \centering
  \includegraphics[width=5.5cm]{../Figs/g1_slice_large.eps}
  \includegraphics[width=5.5cm]{../Figs/g1_slice_small.eps}
  \includegraphics[width=5.5cm]{../Figs/g2_slice.eps}
  \caption{\label{glycerolNMR}
    R-PDFL slices for gycerol backbone carbons.
  }
  \todo{We need nicer figure for this data. Maybe combine with \ref{PShgSIGNSsimpson}} \\
  \todo{What are the top figures actually?}
\end{figure}

@@

>>>>

Figure \ref{PShgSIGNSsimpson} summarizes the experimental NMR results for POPS bilayer sample.
showing one single
    splitting for beta (which gives an order parameter equal to 0.12), and for alpha a superposition
    of a large splitting (order parameter equal to 0.09) and a very small splitting which cannot
    resolved with the available resolution.
    S-DROSS slice for beta clearly shows that the order parameter is negative,
    which is confirmed by SIMPSON simulations using the 
    The S-DROSS slice for alpha suggests that the higher order parameter is positive
    and the deviation towards negative values in the longer t1 times suggests
    that the smaller order parameter is negative.
    This is confirmed by SIMPSON simulation using value of 0.09
    for the larger alpha order parameter and the value of -0.02 for
    smaller (black curve). The value for the smaller
    alpha order parameter for SIMPSON calculation was taken from Fig 3 in Ref. \citenum{roux91},
    because resolution in 13C NMR experiments was nor high enough to determine
    numerical value for this. The S-DROSS curve from SIMPSON simulation with positive value
    for the smaller order parameter (dashed grey), did not agree with experiments 
    confirming the interpretation that the smaller order parameter is negative.
\begin{figure}[!htb]
  \centering
  \includegraphics[width=8.5cm]{../scratch/figIDEA.eps}
  \caption{\label{PShgSIGNSsimpson}
    (a) The headgroup region of the INEPT spectrum with headgroup and glycerol backbone carbons assigned.
    (b) 2D R-PDLF spectra for headgroup and glycerol backbone regions.
    (c) Slices for $\alpha$ and $\beta$ barbons.
    (d) Experimental SDROSS data (points) and SIMPSON simulations (lines).
    Order parameter values of -0.12 for the $\beta$-carbon, and 0.09 and -0.02
    for the larger and smaller $\alpha$-carbon slittings were used in the
    SIMPSON calculations. The S-DROSS curve from SIMPSON simulation with positive value
    for the smaller order parameter (dashed grey).
  }
  \todo{This is preliminary figure, should be polished.}
  \todo{Should we show slices for all the analyzed carbons in (c)?}
\end{figure}

%\begin{figure}[!htb]
%  \centering
%  \includegraphics[width=5.5cm]{../Figs/g1_slice_large.eps}
%  \includegraphics[width=5.5cm]{../Figs/g1_slice_small.eps}
%  \includegraphics[width=5.5cm]{../Figs/g2_slice.eps}
%  \caption{\label{glycerolNMR}
%    R-PDFL slices for gycerol backbone carbons.
%  }
%  \todo{We need nicer figure for this data. Maybe combine with \ref{PShgSIGNSsimpson}} \\
%  \todo{What are the top figures actually?}
%\end{figure}

@@

\section{Difference between POPC and OPPS in MacRog model}

\begin{figure}[]
  \centering
  \includegraphics[width=9.0cm]{../Figs/HGorderparametersPOPSvsOPPS.eps}
  \caption{\label{CHANGESwithCaClPGPS}
    Headgroup order parameters from POPS and OPPS simulations with MacRog model.}
\end{figure}
